A Domain Specific Language for SpectreGuard

### 2020-12-07 paper/main.tex
Reflect proper array type generation in paper

\begin{figure}
\begin{lstlisting}{language=C}
int* _fs_0[8] __attribute__((nospec))__;
int* _fs_1[8];
for (int _fs_2 = 0; _fs_2 < 8; _fs_2 = _fs_2 + 1) {
  int _fs_3 = 0;
  for (int _fs_4 __attribute__((nospec))__ = 0;
       _fs_4 < (_fs_0[_fs_2]);
       _fs_4 = _fs_4 + 1) {
    _fs_3 = _fs_3 + 1;
  }
  _fs_1[_fs_2] = _fs_3;
}
\end{lstlisting}
\caption{C code generated from \ttt{example4}}
\label{fig:GenC4}
\end{figure}

@@

\begin{table}
  \centering
  \begin{tabular}{|c|c|}
    \hline
    EDSL name & Generated C Name \\
    \hline
    \verb|secretArray| & \verb|_fs_0|\\
    \verb|publicArray| & \verb|_fs_1|\\
    \verb|leak| & \verb|_fs_3|\\
    \verb|secretArrayA| & \verb|_fs_5|\\
    \verb|secretArrayB| & \verb|_fs_6|\\
    \verb|publicArray2| & \verb|_fs_7|\\
    \verb|leak2| & \verb|_fs_9|\\
    \hline
  \end{tabular}
\caption{Correspondence between EDSL names and generated C names for \ttt{example5}}
\label{table:Names5}
\end{table}

>>>>

\begin{figure}
\begin{lstlisting}{language=C}
int _fs_0[8] __attribute__((nospec))__;
int _fs_1[8];
for (int _fs_2 = 0; _fs_2 < 8; _fs_2 = _fs_2 + 1) {
  int _fs_3 = 0;
  for (int _fs_4 __attribute__((nospec))__ = 0; _fs_4 < (_fs_0[_fs_2]); _fs_4 = _fs_4 + 1) {
    _fs_3 = _fs_3 + 1;
  }
  _fs_1[_fs_2] = _fs_3;
}
\end{lstlisting}
\caption{C code generated from \ttt{example4}}
\label{fig:GenC4}
\end{figure}

@@

\begin{table}
  \centering
  \begin{tabular}{|c|c|}
    \hline
    EDSL name in \ttt{example5} & Generated C Name \\
    \hline
    \verb|secretArray| & \verb|_fs_0|\\
    \verb|publicArray| & \verb|_fs_1|\\
    \verb|leak| & \verb|_fs_3|\\
    \verb|secretArrayA| & \verb|_fs_5|\\
    \verb|secretArrayB| & \verb|_fs_6|\\
    \verb|publicArray2| & \verb|_fs_7|\\
    \verb|leak2| & \verb|_fs_9|\\
    \hline
  \end{tabular}
\caption{Correspondence between EDSL names and generated C names for \ttt{example5}}
\label{table:Names5}
\end{table}
